Constructive Preference Elicitation by Setwise Max-margin Learning

### 2016-01-18 paper/ijcai16.tex
paper: update the plots with the latest figures.

\begin{figure}[b]
    \centering
    \begin{tabular}{ccc}
        {\bf synthetic 3} & {\bf synthetic 4} & {\bf synthetic 5}
        \\
        \includegraphics[width=12em]{figures/synthetic_3_uniform} &
        \includegraphics[width=12em]{figures/synthetic_4_uniform} &
        \includegraphics[width=12em]{figures/synthetic_5_uniform}
        \\
        \includegraphics[width=12em]{figures/synthetic_3_uniform_sparse} &
        \includegraphics[width=12em]{figures/synthetic_4_uniform_sparse} &
        \includegraphics[width=12em]{figures/synthetic_5_uniform_sparse}
        \\
        \includegraphics[width=12em]{figures/synthetic_3_normal} &
        \includegraphics[width=12em]{figures/synthetic_4_normal} &
        \includegraphics[width=12em]{figures/synthetic_5_normal}
        \\
        \includegraphics[width=12em]{figures/synthetic_3_normal_sparse} &
        \includegraphics[width=12em]{figures/synthetic_4_normal_sparse} &
        \includegraphics[width=12em]{figures/synthetic_5_normal_sparse}
    \end{tabular}
    \caption{Results on the synthetic dataset. Each row represents a different
    setting: uniform, uniform sparse, normal, normal sparse. Color indicates
    the set size $k$: blue means $k=2$, greed $k=3$, and red $k=4$.}
\end{figure}

>>>>

\begin{figure}[b]
    \centering
    \begin{tabular}{cccc}
        {\bf synthetic 3} & {\bf synthetic 4} & {\bf synthetic 5} & {\bf synthetic 6}
        \\
        \includegraphics[width=12em]{figures/synthetic_3_uniform_cv1_loss} &
        \includegraphics[width=12em]{figures/synthetic_4_uniform_cv1_loss} &
        \includegraphics[width=12em]{figures/synthetic_5_uniform_cv1_loss} &
        \includegraphics[width=12em]{figures/synthetic_6_uniform_cv1_loss}
        \\
        \includegraphics[width=12em]{figures/synthetic_3_uniform_sparse_cv1_loss} &
        \includegraphics[width=12em]{figures/synthetic_4_uniform_sparse_cv1_loss} &
        \includegraphics[width=12em]{figures/synthetic_5_uniform_sparse_cv1_loss} &
        \includegraphics[width=12em]{figures/synthetic_6_uniform_sparse_cv1_loss}
        \\
        \includegraphics[width=12em]{figures/synthetic_3_normal_cv1_loss} &
        \includegraphics[width=12em]{figures/synthetic_4_normal_cv1_loss} &
        \includegraphics[width=12em]{figures/synthetic_5_normal_cv1_loss} &
        \includegraphics[width=12em]{figures/synthetic_6_normal_cv1_loss}
        \\
        \includegraphics[width=12em]{figures/synthetic_3_normal_sparse_cv1_loss} &
        \includegraphics[width=12em]{figures/synthetic_4_normal_sparse_cv1_loss} &
        \includegraphics[width=12em]{figures/synthetic_5_normal_sparse_cv1_loss} &
        \includegraphics[width=12em]{figures/synthetic_6_normal_sparse_cv1_loss}
    \end{tabular}
    \caption{Results on the synthetic dataset, with crossvalidation at each step. Each row represents a different
    setting: uniform, uniform sparse, normal, normal sparse. Color indicates
    the set size $k$: orange means $k=2$, blue $k=3$, and violet $k=4$.}
\end{figure}

\begin{figure}[b]
    \centering
    \begin{tabular}{cccc}
        {\bf synthetic 3} & {\bf synthetic 4} & {\bf synthetic 5} & {\bf synthetic 6}
        \\
        \includegraphics[width=12em]{figures/synthetic_3_uniform_cv5_loss} &
        \includegraphics[width=12em]{figures/synthetic_4_uniform_cv5_loss} &
        \includegraphics[width=12em]{figures/synthetic_5_uniform_cv5_loss} &
        \includegraphics[width=12em]{figures/synthetic_6_uniform_cv5_loss}
        \\
        \includegraphics[width=12em]{figures/synthetic_3_uniform_sparse_cv5_loss} &
        \includegraphics[width=12em]{figures/synthetic_4_uniform_sparse_cv5_loss} &
        \includegraphics[width=12em]{figures/synthetic_5_uniform_sparse_cv5_loss} &
        \includegraphics[width=12em]{figures/synthetic_6_uniform_sparse_cv5_loss}
        \\
        \includegraphics[width=12em]{figures/synthetic_3_normal_cv5_loss} &
        \includegraphics[width=12em]{figures/synthetic_4_normal_cv5_loss} &
        \includegraphics[width=12em]{figures/synthetic_5_normal_cv5_loss} &
        \includegraphics[width=12em]{figures/synthetic_6_normal_cv5_loss}
        \\
        \includegraphics[width=12em]{figures/synthetic_3_normal_sparse_cv5_loss} &
        \includegraphics[width=12em]{figures/synthetic_4_normal_sparse_cv5_loss} &
        \includegraphics[width=12em]{figures/synthetic_5_normal_sparse_cv5_loss} &
        \includegraphics[width=12em]{figures/synthetic_6_normal_sparse_cv5_loss}
    \end{tabular}
    \caption{Results on the synthetic dataset, with crossvalidation every 5 steps. Each row represents a different
    setting: uniform, uniform sparse, normal, normal sparse. Color indicates
    the set size $k$: orange means $k=2$, blue $k=3$, and violet $k=4$.}
\end{figure}

\begin{figure}[b]
    \centering
    \begin{tabular}{cccc}
        {\bf synthetic 3} & {\bf synthetic 4} & {\bf synthetic 5} & {\bf synthetic 6}
        \\
        \includegraphics[width=12em]{figures/synthetic_3_uniform_cv1_time} &
        \includegraphics[width=12em]{figures/synthetic_4_uniform_cv1_time} &
        \includegraphics[width=12em]{figures/synthetic_5_uniform_cv1_time} &
        \includegraphics[width=12em]{figures/synthetic_6_uniform_cv1_time}
        \\
        \includegraphics[width=12em]{figures/synthetic_3_uniform_sparse_cv1_time} &
        \includegraphics[width=12em]{figures/synthetic_4_uniform_sparse_cv1_time} &
        \includegraphics[width=12em]{figures/synthetic_5_uniform_sparse_cv1_time} &
        \includegraphics[width=12em]{figures/synthetic_6_uniform_sparse_cv1_time}
        \\
        \includegraphics[width=12em]{figures/synthetic_3_normal_cv1_time} &
        \includegraphics[width=12em]{figures/synthetic_4_normal_cv1_time} &
        \includegraphics[width=12em]{figures/synthetic_5_normal_cv1_time} &
        \includegraphics[width=12em]{figures/synthetic_6_normal_cv1_time}
        \\
        \includegraphics[width=12em]{figures/synthetic_3_normal_sparse_cv1_time} &
        \includegraphics[width=12em]{figures/synthetic_4_normal_sparse_cv1_time} &
        \includegraphics[width=12em]{figures/synthetic_5_normal_sparse_cv1_time} &
        \includegraphics[width=12em]{figures/synthetic_6_normal_sparse_cv1_time}
    \end{tabular}
    \caption{Results on the synthetic dataset, with crossvalidation at each step. Each row represents a different
    setting: uniform, uniform sparse, normal, normal sparse. Color indicates
    the set size $k$: orange means $k=2$, blue $k=3$, and violet $k=4$.}
\end{figure}

\begin{figure}[b]
    \centering
    \begin{tabular}{cccc}
        {\bf synthetic 3} & {\bf synthetic 4} & {\bf synthetic 5} & {\bf synthetic 6}
        \\
        \includegraphics[width=12em]{figures/synthetic_3_uniform_cv5_time} &
        \includegraphics[width=12em]{figures/synthetic_4_uniform_cv5_time} &
        \includegraphics[width=12em]{figures/synthetic_5_uniform_cv5_time} &
        \includegraphics[width=12em]{figures/synthetic_6_uniform_cv5_time}
        \\
        \includegraphics[width=12em]{figures/synthetic_3_uniform_sparse_cv5_time} &
        \includegraphics[width=12em]{figures/synthetic_4_uniform_sparse_cv5_time} &
        \includegraphics[width=12em]{figures/synthetic_5_uniform_sparse_cv5_time} &
        \includegraphics[width=12em]{figures/synthetic_6_uniform_sparse_cv5_time}
        \\
        \includegraphics[width=12em]{figures/synthetic_3_normal_cv5_time} &
        \includegraphics[width=12em]{figures/synthetic_4_normal_cv5_time} &
        \includegraphics[width=12em]{figures/synthetic_5_normal_cv5_time} &
        \includegraphics[width=12em]{figures/synthetic_6_normal_cv5_time}
        \\
        \includegraphics[width=12em]{figures/synthetic_3_normal_sparse_cv5_time} &
        \includegraphics[width=12em]{figures/synthetic_4_normal_sparse_cv5_time} &
        \includegraphics[width=12em]{figures/synthetic_5_normal_sparse_cv5_time} &
        \includegraphics[width=12em]{figures/synthetic_6_normal_sparse_cv5_time}
    \end{tabular}
    \caption{Results on the synthetic dataset, with crossvalidation every 5 steps. Each row represents a different
    setting: uniform, uniform sparse, normal, normal sparse. Color indicates
    the set size $k$: orange means $k=2$, blue $k=3$, and violet $k=4$.}
\end{figure}
